---
output: html_document
---
Statistical Inference Project 2
===============================
by `EricRybicki`

# Basic inferential data analysis

In this case we will explore the effect of Vitamin C on tooth growth in Guinea Pig.

## Load and Exploratory Analysis

```{r}
library(datasets)
?ToothGrowth
```
### Description
The response is the length of odontoblasts (teeth) in each of 10 guinea pigs at each of three dose levels of Vitamin C (0.5, 1, and 2 mg) with each of two delivery methods (orange juice or ascorbic acid).

#### Format
A data frame with 60 observations on 3 variables.

`[,1] len	numeric	Tooth length`

`[,2] supp	factor	Supplement type (VC or OJ).`

`[,3] dose	numeric	Dose in milligrams.`

```{r}
tooth <- ToothGrowth
str(tooth)
head(tooth)
```

## Provide a basic summary of the data.
```{r}
library(knitr)
kable(summary(tooth))
```

```{r plot_1, fig.width = 10}
library(ggplot2)
g <- ggplot(tooth, aes(as.factor(dose), len, fill = supp))
g <- g + geom_bar(stat="identity", position = "dodge") + theme_bw()
g <- g + scale_fill_manual("Teams",values = c("#ff6666", "#33cc33"), guide = guide_legend(title = "Supplement"))
g <- g + xlab("Dose in milligrams") + ylab("Tooth Length")
g
```

## Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose.
```{r}
t.test(len ~ supp, data = tooth)
```
From confidence intervals containing zero and p-value of 0.06, we cannot assume that there are differences in tooth growth due to OJ and VC supplements.

```{r}
tooth_0.5_1.0 <- subset(tooth, dose %in% c(0.5, 1.0))
t.test(len ~ supp, tooth_0.5_1.0)
tooth_0.5_2.0 <- subset(tooth, dose %in% c(0.5, 2.0))
t.test(len ~ supp, tooth_0.5_2.0)
tooth_1.0_2.0 <- subset(tooth, dose %in% c(1.0, 2.0))
t.test(len ~ supp, tooth_1.0_2.0)
```

From the selection of t.tests on dosage pairs we can note the low p-values and non-zero confidence values. As a consequence we can confirm that the key component of tooth growth, with regard to supplements, is dosage. 

## Conclusion

To recap, based on the analysis above, we can conclude that across both supplements a higher dosage will have a higher tooth growth rate. However, we cannot say that orange juice and vitamin C have obvious different impact on tooth growth.

